Parallel multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-09-14 hpmoon-hpca.tex
Explaining real problem for issue #3

\subsection{Real problem}
\textcolor{red}{A real problem has also been used.}

>>>>

\subsection{Real problem benchmark: Unsupervised Feature Selection}
\textcolor{red}{A real problem has also been used to BLABLABLA. In this case, the problem used to solve is the unsupervised feature selection. A dataset formed by EEG signals from Brain Computer Interface (BCI) is used as a benchmark \cite{Kimovski15Parallel}, due to the required high computational cost and chromosome length. Individuals in this case are binary vectors indicating if a specific feature is selected or not. To evaluate a set of features different clustering validation indexes (CVIs) can be used.}

\textcolor{red}{In this case, the two objectives to compare the three methods are the inter-cluster separation ($f1$) and the intra-cluster separation ($f2$). To obtain this measures, and after applying the projection to the dataset, a method based in the one presented  \cite{Kimovski15Parallel} is applied. Starting with a random value of the projection, the distance to the closer one is stored, and so on. After ordering these distances from lower to higher, we consider the intra-cluster distance ($f1$) as the one in the position 1/4 of the list, while the inter-cluster ($f2$) distance is in the position 3/4. The intra-cluster distance objective needs to be minimized, while the inter-cluster is maximized. Figure \ref{fig:cvis} explains this method using a extremely simplified example. Note that the goal of this paper is not obtain better CVI values than other methods, but to study the different overlapping schemes in parallel MOEAs.}

\begin{figure}
\centering
\includegraphics[width=10cm]{clusterCVI.pdf}
\caption{\textcolor{red}{Method to calculate the two objectives for the Feature Selection problem. Starting from a random $d$ point of the projection of the features, the distance to the closer point is calculated iteratively. After ordering these distances, the one in the position 1/4 (a) is considered the intra-cluster distance, while the one in position 3/4 (b) is considered the inter-cluster one.}}
\label{fig:cvis}
\end{figure}

\textcolor{red}{The Dataset used is ... Due to the high computational cost required for the fitness function, the running time for each run has been set to 4 hours, with two generations before sending the individual to another random island. Table \ref{tab:parametersBCI} summarizes the specific parameters for this experiment (the rest of the parameters are the same than the previous experiment, shown in Table \ref{tab:parameters} ). As there is no optimal PF known for this problem, we have used the paretos obtained from all runs to obtain the optimal PF to apply the IGD quality metric.}

\textcolor{red}{
\begin{table*}
\begin{center}
\begin{tabular}{|c|c|}
\hline
{\em Parameter Name} & {\em Value} \\ \hline
Number of islands ($P$) & 8, 32 and 128 \\ \hline
Chromosome size ($L$) & 3600 \\ \hline
Crossover type & One-point \\ \hline
Mutation  type & flip\\ \hline
Generations between migration & 2 \\ \hline
Runs per configuration & 10 \\ \hline
\end{tabular}
\caption{\textcolor{red}{Parameters and operators used in the experiments for Feature Selection problem (the rest of the parameters are the ones described in Table \ref{tab:parameters}).}}
\label{tab:parametersBCI}
\end{center}
\end{table*}
}
